Behavior Driven Development in Haskell

### 2012-05-28 paper.tex
small change for intro.
Do not use "evidence for developers"

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.
For this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation,
we make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to it.

@@

To describe evidence for developers, we can use Hspec.
Hspec provides an EDSL for defining specs.  A spec organizes evidence in a
tree structure, and it is defined with \texttt{it} and \texttt{describe}.

@@

>>>>

In BDD, all behavior should be documented, together with some
\emph{evidence} for that behavior.
For this purpose, 
we brought a test method from other programming language community and
extended missing features.
In particular, we introduced Doctest~\cite{doctest} and
integrated it with QuickCheck~\cite{quickcheck}
for user documentation.
For code documentation,
we make use of Hspec inspired by RSpec~\cite{rspec}
and we proposed some combinators to set expectations
about \emph{code example}\/s.

@@

If we have evidence that does not fit into the user documentation, but
would rather be part of a design document, we use Hspec.  Hspec
provides an EDSL for defining specs.  A spec organizes evidence in a
tree structure, and it is defined with \texttt{it} and
\texttt{describe}.

@@

\emph{TBD What does this have to do with the topic of the paper?}
